Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-04 WSSSPE1_report/WSSSPE1_summary_report.tex
Refined Section 1. Intro

Because progress in scientific research is dependent on the quality
and accessibility of software at all levels, it is now critical to
address many challenges related to the development, deployment, and
maintenance of reusable software. In addition, it is essential that
scientists, researchers, and students are able to learn and adopt
software-related skills and methodologies. Established researchers are
already acquiring some of these skills, and in particular a
specialized class of software developers is emerging in academic
environments who are an integral and embedded part of successful
research teams. The WSSSPE workshop was intended to provide a forum
for discussion of the challenges, including both positions and
experiences.  The short papers and discussion have been archived to
provide a basis for continued discussion, and the workshop has fed
into the collaborative writing of this journal publication.
Additional papers based on extended versions of workshop submissions
are expected.  The level of interest in the workshop has led the
organizers, working with some of the submitters and some of the
attendees, to plan two additional workshops (at the 2014 SciPy and SC
conferences) and to turn the workshop website into a community website
that can be used as a focus for further discussion and progress.

@@

\todo{Mention a two-session minisymposium on ``Reliable Computational
  Science'' in the SIAM Annual Meeting in July. It aims to further
  explore some of the key issues raised in WSSSPE. Speakers include
  Tim Davis, Barry Smith, Lorena Barba, Tanu Malik, Bill Rider.}

>>>>

Because progress in scientific research is dependent on the quality
and accessibility of software at all levels, it is now critical to
address many challenges related to the development, deployment, and
maintenance of reusable software. In addition, it is essential that
scientists, researchers, and students are able to learn and adopt
software-related skills and methodologies. Established researchers are
already acquiring some of these skills, and in particular a
specialized class of software developers is emerging in academic
environments who are an integral and embedded part of successful
research teams. The WSSSPE workshop was intended to provide a forum
for discussion of the challenges, including both positions and
experiences.  The short papers and discussion have been archived to
provide a basis for continued discussion, and the workshop has fed
into the collaborative writing of this journal publication.
Additional papers based on extended versions of workshop submissions
are expected.  The level of interest in the workshop has led the
organizers, working with some of the submitters and attendees, to plan
two additional workshops (at the 2014 SciPy and SC conferences) and to
turn the workshop website into a community website that can be used as
a focus for further discussion and progress.  A minisymposium on
``Reliable Computational Science'' that aims to further explore some
of the key issues raised in WSSSPE is co-organized by a participant in
the 2014 SIAM Annual Meeting.

@@
